Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-17 Ben_Manuscripts/Masters_Bypass/results.tex
restrained XRD figures
More Figures

\beging{figure}
	\centering
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_layered.png}
		\caption{}\label{fig:p2p_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{thickness_layered.png}
		\caption{}\label{fig:thickness_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{order_layered.png}
		\caption{}\label{fig:order_layered}
	\end{subfigure}
\end{figure}

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short NVT simulations were run with position restraints
on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
generated from each configuration establish a difference between the two
stacking modes. In each pattern, R-alkanes is present at a distance of
$\approx 1.5$ \angstrom \textsuperscript{-1}. R-pi is also present in each 
pattern, although it appears to intersect R-alkanes because the spacing
between aromatic rings is similar to the alkane chain packing. The difference 
in aromatic ring spacing between experiment and simulation is likely a result
of the inability of GAFF to properly handle aromatic interactions. The parallel
displaced configuration contains two lines of high intensity with maximum
intensity occurring where they intersect the alkane chain region due to
constructive interference between the two features. The lines are located
where one would expect to see R-helix. As the simulation is progressed, 
the full line begins to fade and the reflection persists only at the 
intersection with the R-alkanes. Most significantly, the line is no
longer present where R-helix exists and, perhaps coincidentally, the 
intersection with R-alkanes occurs where one would expect to see R-spots.

Full comparison of experimental 2D WAXS with simulated X-ray diffraction
patterns produced from equilibrated MD trajectories shows the most consistency
with the sandwiched conformation in Basin A. Systems were built in both the 
parallel displaced and sandwiched conformations with an intial layer spacing of
3.7 \angstrom. A third system was created by stacking layers in the sandwiched 
conformation 5 \angstrom apart in order to guide it towards Basin B. For ease of
reference, the third system will be referred to as the disordered system. The 
three systems were equilibrated according to our procedure with NPT simulations of 
greater than 400 ns. Simulated diffration patterns were generated using 
portions of the trajectory after equilibration. Equilibration was detected
when the distance between pores and the membrane thickness stopped changing.
Simulated diffraction patterns for all three structures are shown in 
Fig~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
R-alkanes and R-pores in the expected locations. Due to low resolution, making
out the individual spots of R-pores is challenging and can be validated upon
further inspection of the 3D structure factor. R-pi is also present, however it
intersects R-alkanes because it is at a lower q than expected. This can be 
explained by our model's inability to appropriately represent aromatic interactions.
The rings prefer to stack $\approx 4.1 \angstrom$ apart as opposed to 3.7 \angstrom.
R-helix and R-spots are both missing. The line which intersected both of these
features in the restrained simulations faded upon equilibration which suggests
that monomers in the parallel-displaced conformation may not give rise to the 
experimental WAXS pattern seen. Simulated XRD of the sandwiched configuration 
contains all features except for R-helix. Most notably, R-spots appears in the
expected location, which suggests that there is something intrinsic to
the sandwiched packing which gives rise to such features. Finally, the 
disordered structure exhibits R-alkanes and R-pores. R-helix and R-spots are not
present. Given the evidence, the sandwiched configuration with layers spaced
3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.

@@

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{p2p_layered.png}
		\caption{}\label{fig:p2p_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{thickness_layered.png}
		\caption{}\label{fig:thickness_layered}
	\end{subfigure}
	\begin{subfigure}{0.325\textwidth}
		\centering
		\includegraphics[width=\textwidth]{order_layered.png}
		\caption{}\label{fig:order_layered}
	\end{subfigure}
\end{figure}

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short NVT simulations were run with position restraints
on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
generated from each configuration establish a difference between the two
stacking modes (Figure~\ref{fig:XRDrestrained}). In each pattern, R-alkanes is present at a distance of
$\approx 1.5$ \angstrom \textsuperscript{-1}. R-pi is also present in each 
pattern, although it appears to intersect R-alkanes because the spacing
between aromatic rings is similar to the alkane chain packing. The difference 
in aromatic ring spacing between experiment and simulation is likely a result
of the inability of GAFF to properly handle aromatic interactions. The parallel
displaced configuration contains two lines of high intensity with maximum
intensity occurring where they intersect the alkane chain region due to
constructive interference between the two features. The lines are located
where one would expect to see R-helix. As the simulation is progressed, 
the full line begins to fade and the reflection persists only at the 
intersection with the R-alkanes. Most significantly, the line is no
longer present where R-helix exists and, perhaps coincidentally, the 
intersection with R-alkanes occurs where one would expect to see R-spots.

\begin{figure}
	\centering
	\begin{subfigure}{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{rzlayeredrestrained.png}
		\caption{}\label{fig:rzplayeredrestrained}
	\end{subfigure}
	\begin{subfigure}{0.475\textwidth}
		\centering
		\includegraphics[width=\textwidth]{rzoffsetrestrained.png}
		\caption{}\label{fig:rzoffsetrestrained}
	\end{subfigure}
	\caption{}\label{fig:XRDrestrained}
\end{figure}

Full comparison of experimental 2D WAXS with simulated X-ray diffraction
patterns produced from equilibrated MD trajectories shows the most consistency
with the sandwiched conformation in Basin A. Systems were built in both the 
parallel displaced and sandwiched conformations with an intial layer spacing of
3.7 \angstrom. A third system was created by stacking layers in the sandwiched 
conformation 5 \angstrom apart in order to guide it towards Basin B. For ease of
reference, the third system will be referred to as the disordered system. The 
three systems were equilibrated according to our procedure with NPT simulations of 
greater than 400 ns. Simulated diffration patterns were generated using 
portions of the trajectory after equilibration (Figure~\ref{fig:XRDsim}). Equilibration was detected
when the distance between pores and the membrane thickness stopped changing.
Simulated diffraction patterns for all three structures are shown in 
Fig~\ref{fig:XRDsim}. The equilibrated parallel displaced structure exhibits 
R-alkanes and R-pores in the expected locations. Due to low resolution, making
out the individual spots of R-pores is challenging and can be validated upon
further inspection of the 3D structure factor. R-pi is also present, however it
intersects R-alkanes because it is at a lower q than expected. This can be 
explained by our model's inability to appropriately represent aromatic interactions.
The rings prefer to stack $\approx 4.1 \angstrom$ apart as opposed to 3.7 \angstrom.
R-helix and R-spots are both missing. The line which intersected both of these
features in the restrained simulations faded upon equilibration which suggests
that monomers in the parallel-displaced conformation may not give rise to the 
experimental WAXS pattern seen. Simulated XRD of the sandwiched configuration 
contains all features except for R-helix. Most notably, R-spots appears in the
expected location, which suggests that there is something intrinsic to
the sandwiched packing which gives rise to such features. Finally, the 
disordered structure exhibits R-alkanes and R-pores. R-helix and R-spots are not
present. Given the evidence, the sandwiched configuration with layers spaced
3.7 \angstrom apart gives rise to an equilibrated structure closest to experiment.

\begin{figure}
	\centering
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{sandwich_rzplot.png}
		\caption{}\label{fig:sandwich_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{offset_rzplot.png}
		\caption{}\label{fig:offsetrzplot}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\centering
		\includegraphics[width=\textwidth]{disorder_rzplot.png}
		\caption{}\label{fig:disorder_rzplot.png}
	\end{subfigure}
	\caption{}\label{fig:XRDsim}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}
		\caption{}\label{fig:tails_topview}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{centroids_box.png}
		\caption{}\label{fig:centroids}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{angles_traj_layered.png}
		\caption{}\label{fig:angle_distribution}
	\end{subfigure}
	\caption{}\label{fig:tail_packing}
\end{figure}
